---
title: "Codebook"
author: "Puneet Singla"
date: "3/21/2021"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("run_analysis.R")
output <- run_analysis()
```

## Author: Puneet Singla
**This codebook.md is generated from Codebook.Rmd**

## This submission includes following R scripts
### 1. run_analysis.R

The purpose of this R script is to consolidate Test & Training datasets. Following variables & transformations are involved

+ fldrnm_test: Folder location of test files
+ fldrnm_train: Folder location of training files
+ flnm_test: List of all test files
+ flnm_train: List of all training files
+ obj_all: List of all R objects to store consolidated Test & Training data
+ subject: Subject id for each observation
+ ftre_lbl: Variable names for each of the feature vector
+ actv_lbl: Activity labels
+ y_actv_lbl: Each observation with their activity labels
+ X: Matrix of all observations with their feature vectors
+ X_mean_std: Subset of X. Feature variables limited to Mean and Standard Deviation
+ X_mean_std_grp_by: X_mean_std variables converted to data frame with declared group by at Subject & Activity level
+ X_avg_mean_std: Tidy dataset with average of all variables in X_mean_std aggregated at Subject & Activity level

## Data Outputs

1.tidy_dataset.txt: A tidy data set representing average of Mean & Standard deviation features of each variable for each activity and each subject. This file is created from variable - X_avg_mean_std

### Data Dictionary: tidy_dataset

sbj_id: Identifies the subject who performed the activity for each window sample.

Unique Values:

```{r echo=FALSE}
unique(output$sbj_id)
```

actv_nm: Activity name

Unique Values:

```{r echo=FALSE}
unique(output$actv_nm)
```

Metrics:

```{r echo=FALSE}
for(i in 3:dim(output)[2]) {
  print(paste0(names(output)[i],":",round(min(output[,i]),3)," - ",round(max(output[,i]),3)))
}
```